Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

@@

% Throughput prediction
There have been a few works in the past that have studied throughput prediction. However most of the past works~\cite{mirza:sigmetrics2007, bui:ewc2014, liu:globecom2015} did not look at using it for latency sensitive applications which require throughput prediction at fine grained time scales.~\cite{sun:sigcomm2016} is one of the works which predicts throughput for video bitrate selection using a data-driven approach. However, they predict throughput for an epoch of 6 seconds whereas in this work we make predictions for a timescale of up to 2 seconds.~\cite{liu:atc2020} performs throughput estimation at a finer grained resolution to estimate the available bandwidth for each user as well as the total available bandwidth from the AP's perspective. To enable this, the authors of~\cite{liu:atc2020} needed to modify the AP's firmware. In our work however the prediction is done on the client side hence we don't need to perform any modifications on the AP.~\cite{liu:globecom2015} performed a study of various throughput prediction algorithms for mobile networks and found that all of them have the highest accuracy when predicting at a timescale of 100-300 seconds which is again too large of a timescale when considering the type of applications we look at in this work.

>>>>

\comment{results???}

@@

% Throughput prediction
Network throughput prediction has been studied in the past. However most of
the past works~\cite{mirza:sigmetrics2007, bui:ewc2014,
  liu:globecom2015} did not look at using it for latency sensitive
applications which require throughput prediction at fine grained time
scales.
\cite{sun:sigcomm2016} predicts
throughput for video bitrate selection using a data-driven
approach. However, the work predicts throughput for an epoch of 6 seconds,
whereas our work studes making predictions for a timescale between 10 ms to 2
seconds.
\cite{liu:atc2020} performs throughput estimation at a finer
grained resolution \comment{how fine scale???}
to estimate the available bandwidth for each user
as well as the total available bandwidth from the AP's perspective. To
do this, the authors had to modify the
AP's firmware. In contrast in our work, the prediction is done on the
client side hence we do not need to perform any modifications on the
AP.
\cite{liu:globecom2015} studied various throughput
prediction algorithms for mobile networks and found that 
the highest accuracy is achieved when predicting at a timescale of 100-300
seconds which is again too large of a timescale for the
type of applications we consider in this work.
